Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Esthetic update to fig2, commented out fig3, ref'd fig2 instead in proof.

            \node (a2) [below left of = aa,node distance=13mm,xshift=2mm] {};
            \node (aa2) [above left of = a2,node distance=13mm,xshift=-2mm] {};
            \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
            \node (ac2) [fill=gray!70,above left of = ab2,node distance=13mm,xshift=-2mm] {};
            \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
            \node (ba2) [above right of = b2,node distance=13mm,xshift=2mm] {};
            \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
            \node (bc2) [fill=gray!70,above right of = bb2,node distance=13mm,xshift=2mm] {};

@@

            \path[dotted] (a) edge (a1) edge (b1);
            \path (aa) edge (a1) edge (b1) edge (a2) edge (b2)
                (a1) edge (b1)
                (aaa) edge (a2) edge (b2)
                (a2) edge (aa2) edge (ab2)
                (b2) edge (ba2) edge (bb2);
            \path[color=gray!70] (ac2) edge (ab2) edge (aa2)
                (bc2) edge (bb2) edge (ba2);

@@

        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
            \node[fill=black] (a1) {};
            \node[fill=black] (b1) [right of = a1] {};
            \node[fill=black] (c1) [right of = b1] {};
            \node[fill=black] (a2) [below of = a1] {};
            \node[fill=black] (b2) [right of = a2] {};
            \node[fill=black] (c2) [right of = b2] {};
            \node[fill=black] (a3) [below of = a2] {};
            \node[fill=black] (b3) [right of = a3] {};
            \node[fill=black] (c3) [right of = b3] {};

@@

            \path[color=gray!70] (a1) edge (b1) edge (a2)
                (b1) edge (c1)
                (c1) edge (c2)
                (a2) edge (b2) edge (a3)
                (c2) edge (c3)
                (a3) edge (b3)
                (b3) edge (c3);
            \path[line width=0.4mm] (b1) edge (a2) edge (b2) edge (c2)
                (a2) edge (b3)
                (b2) edge (c2) edge (b3)
                (c2) edge (b3);
        \end{tikzpicture}
        \hspace{1cm}
        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
            \node[fill=black] (p) {};
            \node[draw=none] (b) [above of = p,node distance=10mm] {};
            \node[fill=black] (a) [left of = b] {};
            \node[fill=black] (c) [right of = b] {};
            \node[fill=black] (d) [above of = b,node distance=10mm] {};

@@

Figure\ref{fig:nds} illustrates the three cases possible when filtering by neighbourhood degree
sequence.  Removing the top node causes each entry in $\nds(p)$ to be reduced; removing the
left-middle node removes an entry from $\nds(p)$; and removing either of the connected nodes in the
middle layer causes both the size of $\nds(p)$ to be reduced and an entry in $\nds(p)$ to be reduced.

@@

\begin{figure}
    \begin{center}
        \begin{tikzpicture}[every node/.style={circle, inner sep=1mm}]
            \node[fill=black] (p) {};
            \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
            \node[fill=uofglawn] (n2) [above of = p,node distance=12mm] {};
            \node[fill=uofgpumpkin] (n1) [left of = n2] {};
            \node[fill=uofglawn] (n3) [right of = n2] {};
            \node[fill=uofgcobalt] (q) [above of = n2,node distance=12mm] {};
            \path (p) edge (n1) edge (n2) edge (n3)
                (n1) edge (q)
                (n2) edge (n3) edge (q)
                (n3) edge (q);
        \end{tikzpicture}
        \caption{Example of neighbourhood degree filtering cases}
        \label{fig:nds}
    \end{center}
\end{figure}

>>>>

            \node (a2) [below left of = aa,node distance=13mm,xshift=2mm] {};
            \node (aa2) [above left of = a2,node distance=13mm,xshift=-2mm] {};
            \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
            \node (ac2) [fill=gray!50,above left of = ab2,node distance=13mm,xshift=-2mm] {};
            \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
            \node (ba2) [above right of = b2,node distance=13mm,xshift=2mm] {};
            \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
            \node (bc2) [fill=gray!50,above right of = bb2,node distance=13mm,xshift=2mm] {};

@@

            \path[dotted] (a) edge (a1) edge (b1);
            \path (aa) edge (a1) edge (b1) edge (a2) edge (b2)
                (a1) edge (b1)
                (aaa) edge (a2) edge (b2)
                (a2) edge (aa2) edge (ab2)
                (b2) edge (ba2) edge (bb2);
            \path[color=gray!50] (ac2) edge (ab2) edge (aa2)
                (bc2) edge (bb2) edge (ba2);

@@

        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
            \node[fill=gray!50] (a1) {};
            \node[fill=black] (b1) [right of = a1] {};
            \node[fill=gray!50] (c1) [right of = b1] {};
            \node[fill=black] (a2) [below of = a1] {};
            \node[fill=black] (b2) [right of = a2] {};
            \node[fill=black] (c2) [right of = b2] {};
            \node[fill=gray!50] (a3) [below of = a2] {};
            \node[fill=black] (b3) [right of = a3] {};
            \node[fill=gray!50] (c3) [right of = b3] {};

@@

            \path[color=gray!50] (a1) edge (b1) edge (a2)
                (b1) edge (c1)
                (c1) edge (c2)
                (a2) edge (b2) edge (a3)
                (c2) edge (c3)
                (a3) edge (b3)
                (b3) edge (c3);
            \path[line width=0.4mm] (b1) edge (a2) edge (b2) edge (c2)
                (a2) edge (b3)
                (b2) edge (c2) edge (b3)
                (c2) edge (b3);
        \end{tikzpicture}
        \hspace{1cm}
        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
            \node[fill=black] (p) {};
            \node[draw=none] (b) [above of = p,node distance=10mm] {};
            \node[fill=black] (a) [left of = b] {};
            \node[fill=black] (c) [right of = b] {};
            \node[fill=black] (d) [above of = b,node distance=10mm] {};

@@

Figure\ref{fig:klessexample} illustrates the three cases possible when filtering by neighbourhood degree
sequence.  Removing the top node causes each entry in $\nds(p)$ to be reduced; removing the
left-middle node removes an entry from $\nds(p)$; and removing either of the connected nodes in the
middle layer causes both the size of $\nds(p)$ to be reduced and an entry in $\nds(p)$ to be reduced.

@@

% \begin{figure}
%     \begin{center}
%         \begin{tikzpicture}[every node/.style={circle, inner sep=1mm}]
%             \node[fill=black] (p) {};
%             \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
%             \node[fill=uofglawn] (n2) [above of = p,node distance=12mm] {};
%             \node[fill=uofgpumpkin] (n1) [left of = n2] {};
%             \node[fill=uofglawn] (n3) [right of = n2] {};
%             \node[fill=uofgcobalt] (q) [above of = n2,node distance=12mm] {};
%             \path (p) edge (n1) edge (n2) edge (n3)
%                 (n1) edge (q)
%                 (n2) edge (n3) edge (q)
%                 (n3) edge (q);
%         \end{tikzpicture}
%         \caption{Example of neighbourhood degree filtering cases}
%         \label{fig:nds}
%     \end{center}
% \end{figure}
